### 2017-01-12 paper/benchmarks.tex

\section{Benchmarks}
\fixme{needed for this version of the paper? we have to find better benchmarks anyways}

>>>>

\section{Benchmarks}
To check performance of our new parallel arrow API, we conducted some benchmarks. These are based on a sudoku solver from the examples for Simon Marlows book "Parallel and Concurrent Programming in Haskell" which can be found on his GitHub \cite{marlow_parconc}. The results are displayed in the following graphs which are ordered by problem size.
\\\\
The Benchmarks were run on a Core i7-3970X CPU @ 3.5GHz with 6 cores and 12 threads. All versions were run 100 times. The resulting running-times were then averaged.
\\
\begin{tikzpicture}
\begin{axis}[
xbar, xmin=0,
width=12cm, height=7cm, enlarge y limits=0.5,
xlabel={avg. seconds run on sudoku17.1000.txt (100 runs)},
symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
ytick=data,
nodes near coords, nodes near coords align={horizontal},
]
\addplot coordinates {(.215,parrows-sudoku-farmChunk) (.213,parrows-sudoku-farm) (.188,parrows-sudoku-parmapstream) (.197,parrows-sudoku-parmap) (.527,parmonad-sudoku-parmap) (1.338,sudoku-sequential)};
\end{axis}
\end{tikzpicture}
\textit{Note: the bad result for parmonad-sudoku-parmap seems to be a artefact as it performs much better in the other benchmarks}
\\\\
\begin{tikzpicture}
\begin{axis}[
xbar, xmin=0,
width=12cm, height=7cm, enlarge y limits=0.5,
xlabel={avg. seconds run on sudoku17.16000.txt (100 runs)},
symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
ytick=data,
nodes near coords, nodes near coords align={horizontal},
]
\addplot coordinates {(3.218,parrows-sudoku-farmChunk) (3.148,parrows-sudoku-farm) (2.755,parrows-sudoku-parmapstream) (2.860,parrows-sudoku-parmap) (2.936,parmonad-sudoku-parmap) (21.324,sudoku-sequential)};
\end{axis}
\end{tikzpicture}
\begin{tikzpicture}
\begin{axis}[
xbar, xmin=0,
width=12cm, height=7cm, enlarge y limits=0.5,
xlabel={avg. seconds run on sudoku17.49151.txt (100 runs)},
symbolic y coords={parrows-sudoku-farmChunk, parrows-sudoku-farm, parrows-sudoku-parmapstream, parrows-sudoku-parmap, parmonad-sudoku-parmap, sudoku-sequential},
ytick=data,
nodes near coords, nodes near coords align={horizontal},
]
\addplot coordinates {(10.038,parrows-sudoku-farmChunk) (10.151,parrows-sudoku-farm) (8.776,parrows-sudoku-parmapstream) (8.969,parrows-sudoku-parmap) (8.679,parmonad-sudoku-parmap) (60.931,sudoku-sequential)};
\end{axis}
\end{tikzpicture}
\\\\
As we can see, the parallel arrow versions of the program all have around the same speedup as the ParMonad based version. This means that using the \code{ArrowParallel} typeclass doesn't add any real overhead. Also, the slightly worse results for "parrows-sudoku-farm" and "parrows-sudoku-farmChunk" can be explained by either imperfect parameters or by the fact that the benchmarks do not really require the scheduling introduced by the skeletons which in this case introduces unnecessary overhead. This would probably look different if the benchmark would use e.g. a divide and conquer approach to solve the sudoku puzzles.

### 2017-01-12 paper/syntacticSugar.tex

\section{Syntactic Sugar}
To make using our new API a bit easier, we also introduce some syntactic sugar.
We start with \code{|>>>|}, which is basically \code{>>>} on lists of arrows.
\begin{lstlisting}[frame=htrbl]
(|>>>|) :: (Arrow arr) => [arr a b] -> [arr b c] -> [arr a c]
(|>>>|) = zipWith (>>>)
\end{lstlisting}
For the basic Arrow case, we have the \code{***} combinator which allows us to combine two arrows \code{arr a b} and \code{arr c d} into an arrow \code{arr (a, c) (b, d)} which does both computations at once. This can easily be lifted into a parallel computation with \code{parEval2}, but requires a backend which has a implementation that does not require any configuration (hence the \code{()} as the conf parameter in the following code snippet).
\begin{lstlisting}[frame=htrbl]
(|***|) :: (ArrowParallel arr a b (),
	ArrowParallel arr (Maybe a, Maybe c) (Maybe b, Maybe d) (),
	ArrowApply arr) =>
	arr a b -> arr c d -> arr (a, c) (b, d)
(|***|) = parEval2 ()
\end{lstlisting}
With this we can analogously to the serial \code{&&&} define the parallel \code{|&&&|}.
\begin{lstlisting}[frame=htrbl]
(|&&&|) :: (ArrowParallel arr a b (),
	ArrowParallel arr (Maybe a, Maybe a) (Maybe b, Maybe c) (),
	ArrowApply arr) =>
	arr a b -> arr a c -> arr a (b, c)
(|&&&|) f g = (arr $ \a -> (a, a)) >>> f |***| g
\end{lstlisting}

>>>>

\section{Syntactic Sugar}
To make using our new API a bit easier, we also introduce some syntactic sugar.
We start with \code{|>>>|}, which is basically \code{>>>} on lists of arrows.
\begin{lstlisting}[frame=htrbl]
(|>>>|) :: (Arrow arr) => [arr a b] -> [arr b c] -> [arr a c]
(|>>>|) = zipWith (>>>)
\end{lstlisting}
For basic arrows, we have the \code{***} combinator which allows us to combine two arrows \code{arr a b} and \code{arr c d} into an arrow \code{arr (a, c) (b, d)} which does both computations at once. This can easily be translated into a parallel version with \code{parEval2}, but for this we require a backend which has an implementation that does not require any configuration (hence the \code{()} as the conf parameter in the following code snippet).
\begin{lstlisting}[frame=htrbl]
(|***|) :: (ArrowParallel arr a b (),
	ArrowParallel arr (Maybe a, Maybe c) (Maybe b, Maybe d) (),
	ArrowApply arr) =>
	arr a b -> arr c d -> arr (a, c) (b, d)
(|***|) = parEval2 ()
\end{lstlisting}
With this we can analogously to the serial \code{&&&} define the parallel \code{|&&&|}.
\begin{lstlisting}[frame=htrbl]
(|&&&|) :: (ArrowParallel arr a b (),
	ArrowParallel arr (Maybe a, Maybe a) (Maybe b, Maybe c) (),
	ArrowApply arr) =>
	arr a b -> arr a c -> arr a (b, c)
(|&&&|) f g = (arr $ \a -> (a, a)) >>> f |***| g
\end{lstlisting}
